%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,roman]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% modern themes
\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}
\usepackage{fontawesome}
%\usepackage{fontspec}
\usepackage{tabularx}
\usepackage{ragged2e}
% if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.8]{geometry}
\usepackage{multicol}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

\usepackage{import}

\newcommand{\cvdoublecolumn}[2]{%
  \cvitem[0.75em]{}{%
    \begin{minipage}[t]{\listdoubleitemcolumnwidth}#1\end{minipage}%
    \hfill%
    \begin{minipage}[t]{\listdoubleitemcolumnwidth}#2\end{minipage}%
    }%
}
\newcommand{\cvreference}[5]{%
    \textbf{#1}\hfill
    \ifthenelse{\equal{#5}{}}{}{\emailsymbol~\texttt{#5}\newline}% Name
    \ifthenelse{\equal{#2}{}}{}{\addresssymbol~#2\newline}%
    \ifthenelse{\equal{#3}{}}{}{#3\newline}%
    \ifthenelse{\equal{#4}{}}{}{#4\newline}%
}

% personal data
\name{Yun Chen}{TSAI}

\newcommand*{\customcvedu}[7][.25em]{
    \begin{tabular}{@{}l} 
        {\bfseries #4}
      \end{tabular}
      \hfill% move it to the right
      \begin{tabular}{l@{}}
         {\bfseries #5}
      \end{tabular} \\
      \begin{tabular}{@{}l} 
        {\itshape #3}
      \end{tabular}
      \hfill% move it to the right
      \begin{tabular}{l@{}}
         {\itshape #2}
      \end{tabular}
      \ifx&#7&%
      \else{\\%
        \begin{minipage}{\maincolumnwidth}%
          \small#7%
        \end{minipage}}\fi%
      \par\addvspace{#1}
}
  
\newcommand*{\customcventry}[5][.25em]{
  \begin{tabular}{@{}l} 
    {\bfseries #2}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\bfseries #3}
  \end{tabular} 
  %\begin{tabular}{@{}l} 
  %  {\itshape #1}
  %\end{tabular}
  %\hfill% move it to the right
  %\begin{tabular}{l@{}}
  %   {\itshape #2}
  %\end{tabular}
  \ifx&#5&%
  \else{\\%
    \begin{minipage}{\maincolumnwidth}%
      \small#5%
    \end{minipage}}\fi%
  %\par\addvspace{#1}
  }

\newcommand*{\customcvproject}[4][.25em]{
%   \vfill\noindent
  \begin{tabular}{@{}l} 
    {\bfseries #2}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\itshape #3}
  \end{tabular}
  \ifx&#4&%
  \else{\\%
    \begin{minipage}{\maincolumnwidth}%
      \small#4%
    \end{minipage}}\fi%
  \par\addvspace{#1}}

\setlength{\tabcolsep}{12pt}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle
\vspace*{-10mm}

\begin{center}
\begin{tabular}{ c c c c }
 \faEnvelopeO\enspace yctsai@connect.ust.hk & \faGithub\enspace yctsai2727 & \faMobile\enspace +852-54418187\\  
\end{tabular}
\end{center}

\section{SUMMARY}
I am a Year 3 undergraduate student at HKUST, major in applied Mathematics. Experienced in academic research and currently having two research projects conducted under the supervision of professor Shing Yu LEUNG and Amir GOHARSHADY, the reseach area focus on different aspect of scientific computation and theoretical computer science (TCS) respectively. Proficient in programming with C/C++, Python and NodeJS. Planning to pursue a Ph.D. in TCS-related area, reseach insterest especially focus in complexity theory, automata theory and mathematical aspect in algorithm design.

\section{EDUCATION}
{\customcvedu{Expected Graduation: June 2024}{BSc in Applied Mathematics}{Hong Kong University of Science and Technology (HKUST)}{}{}{}}

\section{PUBLICATION}
\begin{itemize}
  \item Conrado, G. K., Goharshady, A. K., Kochekov, K., Tsai, Y. C., Zaher, A. K. (2023).  \textit{In Exploiting the Sparseness of Control-flow and Call Graphs for Efficient and On-demand Algebraic Program Analysis.} submitted to OOPSLA.
\end{itemize}

\section{COURSE TAKEN}

Only selected courses are recorded.\\

{\customcventry{MATH course}{HKUST}{}
{\begin{itemize}
  \item MATH 1023 Honor Calculus I \hfill             grade: A
  \item MATH 1024 Honor Calculus II \hfill            grade: A-
  \item MATH 2043 Honor Mathematical Analysis \hfill  grade: A-
  \item MATH 2431 Honor Probability \hfill            grade: A-
  \item MATH 3043 Honor Real Analysis \hfill          grade: A
\end{itemize}
}}
\\

{\customcventry{COMP course}{HKUST}{}
{\begin{itemize}
  \item COMP 2011 Programming in C++ \hfill           grade: A
  \item COMP 2012 Object-Oriented Programming and Data Structures \hfill    grade: A+
  \item COMP 2711H Honor Discrete Mathematics Tool \hfill grade: A+
  %\item COMP 3711 Design and Analysis of Algorithms \hfill grade: B+
  \item COMP 3721 Theory of computation \hfill grade: A
  \item COMP 5711 Introduction to Advanced Algorithmic Techniques \hfill grade: A+
\end{itemize}
}}
\\

{\customcventry{research course}{HKUST}{}
{\begin{itemize}
  \item UROP 1100 Efficient Algorithm on Visualizing Dynamical Surface \hfill grade: P*
  \item UROP 1100 Parameterized algorithm for static program analysis \hfill grade: P*
  \item UROP 2100 Parameterized algorithm for static program analysis \hfill grade: P*
  \item SCIE 3500 IRE research Project I \hfill grade: A+
\end{itemize}
}}

\newpage
\section{RESEARCH PROJECT}
{\customcventry{Project title}{Supervisor}{}{}
}\enspace\\

{\customcventry{Efficient algorithm on Visualizing Dynamical Surface}{Dr. Shing Yu LEUNG}{}
{\begin{itemize}
  \item In this project we particularly focus on developping efficient methods for visualizing the Lagrangian Coherent Structure. Several approaches have been studied including the traditional Finite time Lyapuonv Exponent, Clustering approach and also comparison between local trajectories. The project is still under progress.
\end{itemize}
}
}\enspace\\

{\customcventry{Parameterized Algorithm and static program analysis}{Dr. Amir GOHARSHADY}{}
{\begin{itemize}
  \item This project is focusing on improving existing method for static program analysis, in particular on automata and model checking. Our main interest is to try to reduce the complexity through parameterization since it has been exposed that most practical system has small treewidth in its control flow graph. Another focus is on the automata side since model checking can be well formulated in terms of LTL logic which is in equivalent with Büchi automata, hence a parameterized algorithm on improving time for verifying several properties like language inclusion and universality would be interesting both theoretically and practically. The project is still under progress.
\end{itemize}
}}

\section{Scholarship}
\begin{itemize}
  \item Chern Class Scholarship
\end{itemize}

\section{Reference}
Please contact the following professors for letter of recommendation.\\

\cvreference{Shing Yu LEUNG}
    {Professor, Department of Mathematics}
    {Hong Kong University of Science and Technology, Clear Water Bay, Hong Kong}
    {}
    {masyleung@ust.hk}


\cvreference{Amir GOHARSHADY}
    {Assistant Professor, Department of Computer Science and Engineering}
    {Hong Kong University of Science and Technology, Clear Water Bay, Hong Kong}
    {}
    {goharshady@cse.ust.hk}

  
% \section{ADDITIONAL}
% \begin{minipage}{\maincolumnwidth}%
% 	\small{
%     	\begin{itemize}
%           \item Programming Languages: C, C++, Javascript, NodeJS, Python
% 		\end{itemize}}%
% \end{minipage}%

%-----       letter       ---------------------------------------------------------

\end{document}


%% end of file `template.tex'.